Title

### 2021-05-28 paper/main.tex
Defined free energy of adsorption

If the potential of mean force ($\mathrm{PMF}$) along $\xi$ has been
estimated for the discrete states $\{\xi_1, \xi_2, ..., \xi_N \}$, the
probability of a state $\xi_{j}$ can be estimated with:

\begin{equation}
\label{eq:A-from-PMF}
p(\xi_j) = \frac{e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}

@@

\begin{equation}
\label{eq:Adsorbed}
p(A) = \frac{\sum_{j \in A} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}
\begin{equation}
\label{eq:Adsorbed}
p(F) = \frac{\sum_{j \in F} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}

Knowing that the probability of a state

>>>>

The free energy of a state is related to the probability of the state
via:

\begin{equation}
\label{eq:A-from-p}
A^i = - k_B T \ln (p_i)
\end{equation}

Where $k_B$ is Boltzmann's constant and T is the
temperature. Replacing Eq.~(\ref{eq:A-from-p}) in
Eq.~(\ref{eq:Adsorption}) we can relate the free energy of adsorption
to the probabilities of the near and free states:

\begin{equation}
\label{eq:Aads-from-p}
\Delta A^{ads} = - k_B T \ln (\frac{p_{near}}{p_{free}})
\end{equation}

If the potential PMF along $\xi$ has been estimated for the discrete
states $\{\xi_1, \xi_2, ..., \xi_N \}$, the probability of a state
$\xi_{j}$ can be estimated with:

\begin{equation}
\label{eq:p-from-PMF}
p_{\xi_j} = \frac{e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}

@@

\begin{equation}
\label{eq:p-near}
p_{near} = \frac{\sum_{j \in near} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}
\begin{equation}
\label{eq:p-free}
p_{free} = \frac{\sum_{j \in free} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}

Replacing Eqs.~(ref{eq:p-near})~and~(\ref{eq:p-free}) in
Eq.\~(\ref{eq:Aads-from-p}) we have an expression to calculate the
free energy of adsorption from a PMF of $\xi$, regardless of how the
PMF was obtained:

\begin{equation}
\label{eq:Aads-from-PMF}
\Delta A^{ads} = - k_B T \ln \left(\frac{\sum_{j \in near} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{k \in free} e^{-\beta~\mathrm{PMF}(\xi_k)}}\right)
\end{equation}

On the following sections, two different methods used to obtain a PMF along $\xi$ will be described.
